\thesistitle{Molecular simulations and binding free energy calculations for drug discovery}

%"Dissertation" for PhD, "Thesis" for master's
\documenttitle{Dissertation}

\degreename{Doctor of Philosophy}

% Use the wording given in the official list of degrees awarded by UCI:
% http://www.rgs.uci.edu/grad/academic/degrees_offered.htm
\degreefield{Pharmacological Sciences}

% Your name as it appears on official UCI records.
\authorname{Nathan M. Lim}

% Use the full name of each committee member.
\committeechair{David L. Mobley}
\othercommitteemembers
{
  Thomas L. Poulos\\
  Douglas J. Tobias
}

\degreeyear{2019}

\copyrightdeclaration
{
  {\copyright} {\Degreeyear} \Authorname
}

% If you have previously published parts of your manuscript, you must list the
% copyright holders; see Section 3.2 of the UCI Thesis and Dissertation Manual.
% Otherwise, this section may be omitted.
% \prepublishedcopyrightdeclaration
% {
% 	Chapter 4 {\copyright} 2003 Springer-Verlag \\
% 	Portion of Chapter 5 {\copyright} 1999 John Wiley \& Sons, Inc. \\
% 	All other materials {\copyright} {\Degreeyear} \Authorname
% }

% The dedication page is optional
% (comment out to exclude).
\dedications
{
  (Optional dedication page)
  
  To ...
}

\acknowledgments
{
Financial support was provided by the National Science Foundation Graduate Research Fellowship (DGE-1321846) and the Molecular Sciences Software Institute (MolSSI) Software Fellowship (ACI-1547580).
%Acknowledge GreenPlanet and TSCC compute time?
}


% Some custom commands for your list of publications and software.
\newcommand{\mypubentry}[3]{
  \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}p{4.5in}r}
    \textbf{#1} & \textbf{#2} \\ 
    \multicolumn{2}{@{\extracolsep{\fill}}p{.95\textwidth}}{#3}\vspace{6pt} \\
  \end{tabular*}
}
\newcommand{\mysoftentry}[3]{
  \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}lr}
    \textbf{#1} & \url{#2} \\
    \multicolumn{2}{@{\extracolsep{\fill}}p{.95\textwidth}}
    {\emph{#3}}\vspace{-6pt} \\
  \end{tabular*}
}

% Include, at minimum, a listing of your degrees and educational
% achievements with dates and the school where the degrees were
% earned. This should include the degree currently being
% attained. Other than that it's mostly up to you what to include here
% and how to format it, below is just an example.
%
% CV is required for PhD theses, but not Master's
% comment out to exclude
\curriculumvitae
{

\textbf{EDUCATION}
  
  \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}lr}
    \textbf{Doctor of Philosophy in Pharmaceutical Sciences} & \textbf{2019} \\
    \vspace{6pt}
    University of California, Irvine & \emph{Irvine, CA} \\
    \textbf{Masters of Science in Pharmaceutical Sciences} & \textbf{2017} \\
    \vspace{6pt}
    University of California, Irvine & \emph{Irvine, CA} \\
    \textbf{Bachelor of Science in Pharmaceutical Sciences} & \textbf{2014} \\
    \vspace{6pt}
    University of California, Irvine & \emph{Irvine, CA} \\
  \end{tabular*}

\vspace{12pt}
\textbf{RESEARCH EXPERIENCE}

  \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}lr}
    \textbf{Graduate Researcher} & \textbf{Sept 2014--Sept 2019} \\
    \vspace{6pt}
    University of California, Irvine & \emph{Irvine, California} \\
  \end{tabular*}
  \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}lr}
    \textbf{Scientific Developer Intern} & \textbf{Jun 2015--Aug 2015} \\
    \vspace{6pt}
    Schrodinger, LLC. & \emph{New York, NY} \\
  \end{tabular*}
   \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}lr}
    \textbf{Scientific Developer Intern} & \textbf{Jun 2014--Sept 2014} \\
    \vspace{6pt}
    Schrodinger, LLC. & \emph{New York, NY} \\
  \end{tabular*} 
   \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}lr}
    \textbf{Undergraduate Researcher} & \textbf{Mar 2013--Sept 2014} \\
    \vspace{6pt}
    Mobley Lab, UCI Dept. of Pharma.Sci. & \emph{Irvine, CA} \\
  \end{tabular*}
   \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}lr}
    \textbf{Undergraduate Researcher} & \textbf{Mar 2013--Jun 2014} \\
    \vspace{6pt}
    Poulos Lab, UCI Dept. of Pharma.Sci. & \emph{Irvine, CA} \\
  \end{tabular*} 

\vspace{12pt}  
\textbf{MENTOR EXPERIENCE}

    \mypubentry{Meghan Osato}{July 2017--Present}{Undergraduate--Biological Sciences \& Computer Science, Spring 2018 UROP Fellowship Awardee}
    \mypubentry{Linh P. Nguyen}{Sept 2016--June 2019}{Undergraduate--Pharmaceutical Sciences, Co-authored 2 Publications} 
  
\pagebreak

\vspace{12pt}
\textbf{PUBLICATIONS}
\begin{enumerate}
    \item \textbf{Lim, N.M.}; Osato, M.; Warren, G.; Mobley, D.L.
        \textit{Fragment pose prediction using non-equilbrium candidate monte carlo and molecular dynamics simulations.}
        In Preparation.
    \item Nguyen, L.P.$^*$; \textbf{Lim, N.M.$^*$}; Warren, G.; Mobley, D.L.
        \textit{Microsecond molecular dynamics simulations for fragment pose prediction.}
        In Preparation.
    \item Nainar, S.; Cuthbert, B.; \textbf{Lim, N.M.}; England, W.; Sophal, K.; Quechol, R.; Mobley, D.L.; Goulding, C.; Spitale, R.C. 
        \textit{An Optimized Chemical-Genetic Method for Cell-Specific Metabolic Labeling of RNA.}
        Submitted 2019 to Nature Methods
    \item Jandova, Z.; Gill, S. C.; \textbf{Lim, N.M.}; Mobley D.L.; and Oostenbrink, C.
        \textit{Binding modes and metabolism of caffeine}
        Submitted 2019 to Journal of Chemical Research and Toxicology
    \item Burley, K.H.; Gill, S.C.; \textbf{Lim, N.M.}; Mobley, D.L.
        \textit{Enhancing Sidechain Rotamer Sampling Using Non-Equilibrium Candidate Monte Carlo.}
        Journal of chemical theory and computation, 15(3), 1848-1862. 2019.
    \item Mobley, D.L.; Bannan, C.C.; Rizzi, A.; Bayly, C.I.; Chodera, J.D.; Lim, V.T.; \textbf{Lim, N.M.}; Beauchamp, K.A.; Slochower, D.R.; Shirts, M.R.; Gilson, M.K.
        \textit{Escaping Atom Types in Force Fields Using Direct Chemical Perception.}
        Journal of Chemical Theory and Computation, 14(11), 6076-6092. 2018.
    \item Gill, S; \textbf{Lim, N.M.}; Grinaway, P.; Rustenburg, A.S.; Fass, J.; Ross, G.; Chodera, J.D.; Mobley, D.L.
        \textit{Binding Modes of Ligands Using Enhanced Sampling (BLUES): Rapid Decorrelation of Ligand Binding Modes Using Nonequilibrium Candidate Monte Carlo.}
        Journal of Chemical Theory and Computation, 14(11), 6076-6092. 2018.
    \item Kyrychenko A.; \textbf{Lim, N.M.}; Freites, J.A.; Nguyen, L.P.; Tobias, D.J.; Mobley, D.L.
        \textit{Refining Protein Penetration into the Lipid Bilayer Using Fluorescence Quenching and Molecular Dynamics Simulations: The Case of Diphtheria Toxin Translocation Domain.}
        Journal of Membrane Biology, 251(3), 379-391. 2018.
    \item \textbf{Lim, N.M} 
        \textit{Molecular Dynamics Ligand FEP Tutorial August 2015}
        Schrödinger Academy, 2015.
    \item Holden, J.K.; Kang, S.; Hollingsworth, S.A.; Li, H.; \textbf{Lim, N.}; Chen, S.; Huang, H.; Xue, F.; Tang, W.; Silverman, R.B; Poulos, T.L.
        \textit{Structure-based design of bacterial nitric oxide synthase inhibitors.}
        Journal of Medicinal Chemistry, 58(2), 994-1004. 2015.
    \item Mobley, D.L.; Liu, S.; \textbf{Lim, N.M.}; Wymer, K.L.; Perryman, A.L.; Forli, S.; Deng, N.; Su, J.; Branson, K.; Olson. A.J.
        \textit{Blind prediction of HIV integrase binding from SAMPL4 challenge.}
        Journal of Computer Aided Molecular Design, 28(4):327-345. 2014.
    \item Mobley, D.L.; Wymer, K.L.; \textbf{Lim, N.M.}; Guthrie, J.P.
        \textit{Blind prediction of solvation free energies from the SAMPL4 challenge.}
        Journal of Computer Aided Molecular Design, 28:135-150. 2014.
    \item Holden, J.K.; \textbf{Lim, N.}; Poulos, T.L.
        \textit{Identification of Redox Partners and Development of a Novel Chimeric Bacterial Nitric Oxide Synthase for Structure Activity Analyses.}
        Journal of Biological Chemistry, 289(42): 29437-29445. 2014.
    \item Liu, S.; Wu, Y.; Lin, T.; Abel, R.; Redmann, J.; Summa, C.M.; Jaber, V.R.; \textbf{Lim, N.M.}; Mobley, D.L.
        \textit{Lead Optimization Mapper: Automating free energy calculations for lead optimization.}
        Journal of Computer Aided Molecular Design, 27(9):755-770. 2013. 
\end{enumerate}

\vspace{12pt}
\textbf{CONFERENCE PUBLICATIONS}

  \mypubentry{Sensitivity in binding free energies due to protein reorganization}{Aug 2016}{Theory and Applications of Computational Chemistry - Seattle}
  \mypubentry{Sensitivity in binding free energies due to protein reorganization}{Mar 2016}{American Chemical Society - San Diego}
  
\vspace{12pt}
\textbf{AWARDS}

  \mypubentry{Phase-II (Investment)}{MolSSI Software Fellowship}
  {The Molecular Sciences Software Institute (MolSSI) provides funding for a set of prestigious fellowships that recognize advanced graduate students and postdocs pursuing the development of software infrastructure, middleware, and frameworks that will benefit the broader field of computational molecular sciences, including biomolecular and macromolecular simulation, quantum chemistry, and materials science. MolSSI Software Fellows receive specialized training in state-of-the- art software design principles and tools, and they engage in outreach and educational efforts organized by the MolSSI.}
  \mypubentry{Phase-I (Seed)}{MolSSI Software Fellowship}
  {“Seed” Fellowships: These six month Fellowships will give recipients the opportunity to work with scientists at the MolSSI in order to implement recommended best practices, putting the Fellow’s project on a firm foundation.}
  \mypubentry{Graduate Research Fellowship}{NSF}
  {The NSF Graduate Research Fellowship Program (GRFP) helps ensure the vitality of the human resource base of science and engineering in the United States and reinforces its diversity. The program recognizes and supports outstanding graduate students in NSF-supported science, technology, engineering, and mathematics disciplines who are pursuing research-based master's and doctoral degrees at accredited United States institutions.}
  
\vspace{12pt}
\textbf{SOFTWARE}

  \mysoftentry{BLUES}{https://github.com/nathanmlim/blues}
  {Applications of nonequilibrium candidate Monte Carlo (NCMC) to ligand binding mode sampling}
  \mysoftentry{OpenMM Orion}{https://github.com/oess/openmm_orion}
  {Cubes and Floes for using OpenMM in Orion}
  

}

% The abstract was previously limited to a maximum of 350 words, 
% but the UCI manual at https://etd.lib.uci.edu/electronic/td2e#2.2.1.
% currently does not indicate that there is any word limit for the abstract
\thesisabstract
{Early stage drug discovery would change dramatically if computational methods could accurately and quickly predict binding modes and affinities of compounds in advance of experiments.
Simulation based approaches like classical molecular dynamics (MD) simulations have gained traction as a useful tool for early stage drug discovery, as MD provides a full atomistic and dynamic view of the biological system of interest.
In principle, MD simulations can be a powerful tool for lead optimization as MD can provide knowledge of the ligand's binding mode, dynamics, and even binding affinity.
In order to accurately compute binding affinities or predict ligand binding modes, simulations must run long enough to capture the relevant biological event or sufficiently sample all the physically relevant conformations.
My research presents the development of new simulation approaches for accelerated sampling and demonstrates the use of non-equilibrium candidate Monte Carlo moves with MD simulations for predicting ligand binding modes to a pharmaceutically relevant target.
}

%%% Local Variables: ***
%%% mode: latex ***
%%% TeX-master: "thesis.tex" ***
%%% End: ***
